Title

### 2014-01-08 paper/parts/methods.tex
Updated paper.
Added note on the coarsening done for the transfer entropy computation,
and added some references for the normalized information comparison.

We can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$). This is the view of a users dynamics taken in \cite{ver2012information} and \cite{darmon2013understanding}. Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case). Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider the only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time. We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$

@@

>>>>

We can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$). This is the view of a user's dynamics taken in \cite{ver2012information} and \cite{darmon2013understanding}. Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case). Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider the only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time. We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$

@@

Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine. We coarsen each time series by considering non-overlapping time intervals ten minutes in length. For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not. Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set. We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour.

### 2014-01-08 paper/parts/results.tex
Updated paper.
Added note on the coarsening done for the transfer entropy computation,
and added some references for the normalized information comparison.

\begin{figure}[h!]
  \centering
\includegraphics[width=0.50\textwidth]{figures/nmi_no_singletons.pdf}
\caption{The normalized mutual information between the communities using the different weightings. Weighting 0 corresponds to the structural (binary weighting) network, weightings 1 through 6 correspond to the weighting using the transfer entropy with lag 1 through 6, weighting 7 corresponds to the hashtag similarity, and weighting 8 corresponds to the retweet-mention weighting. Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity. The normalized mutual information is computed with the singletons removed.}
\label{Fig-compare_coverings}
\end{figure}

>>>>

\subsection{Community Statistics (? A better title should go here.)}

Discuss the basic properties of the various types of communities: distribution of sizes, number of singletons, etc.

\subsection{Comparing Community-Types with Normalized Mutual Information}

Because OSLOM detects \emph{coverings} rather than \emph{partitions} of users, standard cluster comparison methods like variation of information~\cite{meilua2003comparing} are not appropriate. Instead, we use a generalized variation of information measure, the normalized information, first introduced in~\cite{lancichinetti2009detecting}. \textbf{TK: Etc. Put more here about NMI, what it does, and how to interpret it.}

The normalized mutual information between the various community-types are shown in Figure~\ref{Fig-compare_coverings}.

\begin{figure}[h!]
  \centering
\includegraphics[width=0.50\textwidth]{figures/nmi_singletons.pdf}
\caption{The normalized mutual information between the communities using the different weightings. Weighting 0 corresponds to the structural (binary weighting) network, weightings 1 through 6 correspond to the weighting using the transfer entropy with lag 1 through 6, weighting 7 corresponds to the hashtag similarity, and weightings 8, 9, and 10 correspond to the mention, retweet, and mention-retweet weightings. Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity. The normalized mutual information is computed with the singletons removed.}
\label{Fig-compare_coverings}
\end{figure}

\subsection{Comparing Different Flows Across Different Community-Types}
